---
title: "Final Project"
author: "Stat385 Team"
date: "May 10, 2018"
output: html_document
---

Topic: The analysis of the relashionship between number of passneger and 
Airline,
Region, 
Price, 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("shiny")
library("ggplot2")
library("dplyr")
```

Take a look at the dataset
```{r}
air_passenger = read.csv("Air_Traffic_Passenger_Statistics.csv")
head(air_passenger)
summary(air_passenger)

```

The number of the passenger VS. Region:

```{r jj}
#Each of the ggplot correspond to each tabPanel in mainPanel
ggplot(air_passenger)+
  geom_boxplot(aes(x = GEO.Region,y = Passenger.Count))

```


Averge passenger of every Published.Airline:

```{r eval = T}
#DATA Transformation
passenger_count = air_passenger %>%
  group_by(Published.Airline.IATA.Code) %>%
  summarise(passenger = mean(Passenger.Count),
            count = n())

#DATA visulization
ggplot(filter(passenger_count,count<4000),aes(x = count,y = passenger))+
  geom_jitter()+
  geom_smooth(se = F)
```

Domestic && International

```{r}
di = air_passenger %>%
  group_by(GEO.Summary) %>%
  summarise(passenger =sum(Passenger.Count),
            count = n())

print(di)

ggplot(di)+
  geom_bar(aes(x = GEO.Summary,y = passenger),stat = "identity")
```

Interesting conclusion: The number of airlines of international is twice of the domestic one，However the number passenger international is only 1/4 of the demostic`

We guess this is because the international plane is not always full, since the size of international one is larger than demostic one`


Number of passengers VS. Price:

```{r}
price = air_passenger %>%
  group_by(Price.Category.Code) %>%
  summarise(passenger =sum(Passenger.Count),
            count = n())


ggplot(price)+
  geom_bar(aes(x = Price.Category.Code,y = passenger,fill = count),stat = "identity")
```


Simple Linear Regression model: Counting Passenger base on different factors. 

```{r}
lm(Passenger.Count~
     Operating.Airline.IATA.Code + GEO.Summary + GEO.Region + Price.Category.Code,data = air_passenger)
```





